Constraints on the dark matter halo mass of Lyman-alpha emitting galaxies at $z$=3.1 from cosmic variance

### 2013-03-05 paper/ms.tex

\documentclass{emulateapj}
\submitted{{\it Submitted for publication in ApJ Letters}}
\usepackage{multirow,color,wrapfig,ulem}
\usepackage {graphicx}
%\bibliographystyle{apj}
\usepackage{graphics}
\usepackage[dvips]{epsfig}

@@

\shorttitle{LAE halo host mass at z=3.1}
\shortauthors{Mej\'ia et al.}

\begin{document}
\title{Constraints on the dark matter halo mass of Lyman-alpha emitting galaxies at $z$=3.1 from cosmic variance}

\author{
J. E.\ Forero-Romero\altaffilmark{1}, 
J. Mej\'ia \altaffilmark{2}, 
}

\altaffiltext{1}{Departamento de F\'{i}sica, Universidad de los Andes, Cra. 1 No. 18A-10, Edificio Ip, Bogot\'a, Colombia, \email{je.forero@uniandes.edu.co}}
\altaffiltext{2}{XXX}
\date{\today}

@@

\begin{figure}
\begin{center}
%\includegraphics[width=1.00\linewidth,angle=0]{./plots/cum_halos_tex.png}
\caption{ \label{figure:laes_dist} Cumulative mass function of dark
  matter haloes in the $210$ sub-volumes of $46\times 35\times 41$
  $h^{-3}Mpc^{3}$. The variation in the total number of dark matter
  halos per sub-volume  evidences the effect of cosmic variance at
  such sub-volume scale. It is also appreciable the low population
  $\lesssim10^{-3}h^{2}Mpc^{-2}$ of halos with
  $log(M/M_{\odot})>12.0$}. 
\end{center} 
\end{figure}

>>>>

\documentclass[usenatbib]{mn2e} 
\usepackage{amsmath} 
\usepackage{amssymb} 
\usepackage{graphics}
\usepackage{graphicx}
\usepackage{epsfig}  
\def\be{\begin{equation}}
\def\ee{\end{equation}}
\def\ba{\begin{eqnarray}}
\def\ea{\end{eqnarray}}

\newcommand{\apj}{ApJ}  
\newcommand{\apjs}{ApJS}  
\newcommand{\apjl}{ApJL}  
\newcommand{\aj}{AJ}  
\newcommand{\mnras}{MNRAS}  
\newcommand{\mnrassub}{MNRAS accepted}  
\newcommand{\aap}{A\&A}  
\newcommand{\aaps}{A\&AS}  
\newcommand{\araa}{ARA\&A}  
\newcommand{\nat}{Nature}  
\newcommand{\physrep}{PhR}
\newcommand{\pasp}{PASP}    
\newcommand{\pasj}{PASJ}

@@

\begin{document}

\title[Dark Matter Halo Mass for LAEs  at $z=3.1$]{Constraints on the dark matter halo mass of Lyman-alpha emitting galaxies at $z$=3.1 from cosmic variance}
\author[J.E. Forero-Romero and J. Mejia]{
\parbox[t]{\textwidth}{\raggedright Jaime E. Forero-Romero$^{1}$ and Julian Mejia$^{2}$}
\vspace*{6pt}\\
$^{1}$\\
$^{2}$
}

\maketitle

@@

\begin{figure}
\begin{center}
\includegraphics[width=1.00\linewidth,angle=0]{./plots/Fig1.pdf}
\caption{ \label{figure:laes_dist} Cumulative mass function of dark
  matter haloes in the $210$ sub-volumes of $46\times 35\times 41$
  $h^{-3}Mpc^{3}$. The variation in the total number of dark matter
  halos per sub-volume  evidences the effect of cosmic variance at
  such sub-volume scale. It is also appreciable the low population
  $\lesssim10^{-3}h^{2}Mpc^{-2}$ of halos with
  $log(M/M_{\odot})>12.0$}. 
\end{center} 
\end{figure}
